Ultra-compact, widely bandwidth-tunable filter using cascaded silicon photonic contra-directional couplers

### 2015-05-20 CacadedTunableFilter.tex
Wei Merge

@@

\begin{document}
\title{Widely Bandwidth-Tunable Broadband Optical Filter on Silicon}
%\date{14/10/2014}

@@

Optical filters are essential components for optical communication applications such as wavelength-division multiplexing (WDM), signal processing, and dynamic bandwidth allocation \cite{DynamicBW}.
These key devices are now needed in integrated photonic systems, in this case, on the silicon-on-insulator platform (SOI), to achieve the same functions as traditional discrete optical components such as diffractive grating spectrometers. 
Silicon photonics allows for CMOS compatible mass fabrication for low cost, high yield, and large-scale on-chip integration. 
Future high-capacity transmission systems, e.g., applying the super-channel technique, will require a dynamic channel bandwidth allocation over a few hundred gigahertz \cite{jinno2009spectrum}. 
However, large bandwidth tunability is currently only available in bulky bench-top systems. Existing integrated tunable filters, e.g., using microring resonators and MZ interferometers, have relatively small tunable bandwidth (less than 200 GHz)  \cite{ong2013ultra}. 
Also, their free spectral ranges (FSRs) are small, typically less than 10 nm \cite{ong2013ultra}.

>>>>

%\newcommand{\EDIT}{}
\usepackage{ulem}

@@

\begin{document}
\title{Ultra-compact, widely bandwidth-tunable filter using cascaded silicon photonic contra-directional couplers}
%\date{14/10/2014}

@@

%Next-generation optical transmission systems require dynamic, efficient bandwidth allocation  
%Bandwidth tunable optical filters are essential components for optical communication applications such as reconfigurable optical wavelength-division multiplexing (WDM), signal processing, and dynamic bandwidth allocation \cite{DynamicBW}.
%These key devices are now needed in integrated photonic systems, in this case, on the silicon-on-insulator platform (SOI), to achieve the same functions as traditional discrete optical components such as diffractive grating spectrometers. 
Next-generation optical transmission systems applying flexible networking and the super-channel technique will require highly dynamic channel allocation to drastically increase the spectral efficiency and transmission capacity \cite{jinno2009spectrum, geisler2011demonstration}.
%over a few hundred gigahertz \cite{jinno2009spectrum}. 
%bandwidth
Tunable optical filters, reconfigurable in both center wavelength and bandwidth with scalability towards terahertz \cite{geisler2011demonstration}, are essential for these applications.
Such large bandwidth tunability is currently only available in bulky bench-top systems using diffractive grating spectrometers or liquid crystals.
Integrated solutions are desired for lower cost and power consumption.
In particular, silicon photonics  based on the submicron silicon-on-insulator platform allows for CMOS compatible mass fabrication, enabling low cost, high yield, and high-density chip-scale integration.
Existing solutions for tunable  filters on silicon include devices based on microring resonators \cite{DynamicBW, ong2013ultra} and Mach-Zehnder interferometers (MZIs). These devices have relatively small tunable bandwidth (less than 200 GHz) and small free spectral ranges (FSRs) (typically less than 10 nm), not suitable for high-capacity transmission applications.
